### 2025-11-15 thesis/implementation/index.tex
Fix

Queries that fail execution are contained in an                                                                                                                                                   │ │
\texttt{errors} hash set rather than being included in voting buckets. If all                                                                                                                     │ │
candidates fail execution, the voting function fails with an error that                                                                                                                           │ │
contains all collected execution errors to provide diagnostic information to                                                                                                                      │ │
the calling side.

>>>>

Queries that fail execution are contained in an \texttt{errors} hash set rather
than being included in voting buckets. If all candidates fail execution, the
voting function fails with an error that contains all collected execution
errors to provide diagnostic information to the calling side.
